---
title       : BMI Calculator
subtitle    : Course Project of Developing Data Products (Coursera)
author      : Arjhun Hariharan
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## What is BMI?

The body mass index (BMI), is a measure of relative weight based on an individual's mass and height. The body mass index (BMI), is a measure of relative weight based on an individual's mass and height. A frequent use of the BMI is to assess how much an individual's body weight departs from what is normal or desirable for a person of his or her height.

## How is it calculated?

$BMI = weight/(height)^2$
where weight - kilograms (kg) and height - metres (m).

For example:
```{r example}
height=1.60
weight=65
weight/height^2
```

--- .class #id 

## Classification 

The following is the classification according to BMI values :

* BMI less than 15    : Very severely underweight
* BMI from 15 to 16   : Severely underweight
* BMI from 16 to 18.5 : Underweight
* BMI from 18.5 to 25 : Healthy weight
* BMI from 25 to 30   : Overweight
* BMI from 30 to 35   : Moderately Obese  
* BMI from 35 to 40   : Severely Obese
* BMI above 40        : Very severely Obese

--- .class #id 

## How does the app work?

It consists of 2 functions, 'BMI_calc' and 'BMI_category'. 

The 'BMI_calc' function takes the height and weight from thr input as parameters, calculates the BMI score and returns it to be displayed as part of the output.

'BMI_calc' function: 
```{r BMI}
BMI_calc<-function(wt,ht)
{
  ht=ht/100
  BMI = wt/(ht^2)
  BMI
}
```

--- .class #id 

## How does the app work (contd.)?

The function 'BMI_category' calsiifies the BMI score calculated into the corresponding category and returns the category to be displays in the output.

```{r category}
BMI_category<-function(wt,ht)
{
  BMIvalue=BMI_calc(wt,ht)
  if(BMIvalue<15) category = "Very severely underweight"
  else if (BMIvalue<16) category =  "Severely underweight"
  else if (BMIvalue<18.5) category =  "Underweight"
  else if (BMIvalue<25) category =  "Healthy weight"
  else if (BMIvalue<30) category = "overweight"
  else if (BMIvalue<35) category =  "Moderately obese"
  else if (BMIvalue<40) category =  "Severely obese"
  else category = "Very severely obese"
  
  category
}
```
